GPU Efficient Texture Based Bezier Curve Evaluation

### 2015-08-12 Paper/paper.tex
Nearly done with feedback adjustments

    \caption{A rational bezier spline showing cosine in green and sine in red.  The white line is the true value of those functions. \textit{Left:} Evaluated with hardware sampling and then division.  \textit{Right:} Evaluated by reading the control points into the shader program, calculating the curves, and then doing a division.}
    \label{fig:rationalbeziersincos}
  \end{figure}

@@

    \end{tikzpicture}
    \caption{\textit{Left:} Curve evaluted with a single texture read and bilinear texture sampling.  \textit{Middle:} Curve evaluated with two linear texture samples, combined in the shader program.  \textit{Right:} Curve evaluated with three texture samples (one per control point), combined in the shader program.}   
    \label{fig:samplehwsw}
  \end{figure}

@@

TODO: do a test with the cards at work, and put those results here as well!

>>>>

    \caption{Rational Bezier spline vs glsl sin() function.  Sin() values in grey on top of the Bezier spline in red.  Red pixels show where the values do not match. }
    \label{fig:rationalbeziersincos}
  \end{figure}

@@

    \end{tikzpicture}
    \caption{ Quality versus texture read count. \textit{Left:} One Texture Read (one bilinear sample). \textit{Middle:} Two Texture Reads (two linear samples). \textit{Right:} Three Texture Reads (three nearest neighbor samples).}   
    \label{fig:samplehwsw}
  \end{figure}

@@

TODO: Test with at least one other card

The performance characteristics don't change very much based on texture dimensionality. This shows that you can up the degree of the curve by upping the dimension of the texture you store the curve in, without incurring any significant performance costs.
